\documentclass[ALICE,manyauthors]{ALICE_analysis_notes}
%
\input{commands}

\usepackage{rotating}
\usepackage{listings}
\usepackage{subcaption}
\usepackage{hyperref}
%
\begin{document}%
%%%%%%%%%%%%% ptdr definitions %%%%%%%%%%%%%%%%%%%%%
%
%%%%%%%%%%%%%%%  Title page %%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{titlepage}
%
\PHnumber{ALICE-ANA-2016-xxx} 
\PHdate{\today}
%
%%% Put your own title + short title here:
\title{D mesons in jets in pp collisions at $\sqrt{s}=7$~TeV: preliminary figures for Quark Matter 2017}
\ShortTitle{D mesons in jets in pp collisions: preliminary figures for Quark Matter 2017}   % appears on right page headers
%
\author{Salvatore Aiola$^{1}$, Fabio F. Colamaria$^{2}$, Andrea Rossi$^{3}$, Antonio C. O. da Silva$^{4,5}$, Barbara Trzeciak$^{5}$}
\author{
1. Yale University, USA\\
2. University of Bari and INFN, Italy\\
3. University of Padova and INFN, Italy\\
4. Utrecht University, Netherlands\\
5. University of Sao Paulo, Brazil\\
}
\author{Email: salvatore.aiola@cern.ch}
%
\ShortAuthor{ALICE Analysis Note 2016}      % appears on left page headers, do not change
%
\begin{abstract}
The study of the charm content of jets is interesting because up to now
it has eluded a precise quantitative understanding in the framework of perturbative QCD (pQCD).
The charm content of jets is known to arise both from prompt production in the process ${\rm gg\, (q\bar{q})} \rightarrow {\rm c\bar{c}}$, and
from the parton shower of gluons and light-flavor quarks.
Charm hadrons coming from the fragmentation of prompt charm jets 
are expected to carry a larger fraction of the total jet momentum,
as compared to those where the charm content arises later in the
parton shower. Therefore the measurement of charm jet fragmentation functions (FFs) 
can be used to estimate the relative strength of the two mechanisms.
Heavy-flavor jets can also provide important insights into the Quark-Gluon Plasma (QGP)
produced in ultra-relativistic heavy-ion collisions, as heavy quarks are predicted
to interact with the QGP differently compared to light quarks and gluons. 
The aim of the analysis is to extract both the $p_{\rm T}$ spectrum of the D-tagged jets and the jet-momentum fraction of the D mesons. 
We identify D-meson candidates via their hadronic decay channels using topological selections and particle identification.
These D-meson candidates are combined with the other charged tracks reconstructed by the central tracking system, 
using the anti-$k_{\rm T}$ jet-finding algorithm.
We extract the yield of D-tagged jets through an invariant mass analysis of the D-meson candidates associated with each jet, 
in bins of jet $p_{\rm T}$ and momentum fraction carried by the D meson. 
For this analysis we use data collected
by ALICE with minimum bias triggers in pp collisions at 7 TeV.
\end{abstract}
\end{titlepage}
%
\tableofcontents
\newpage
\input{content.tex}               %%%%%%%%%%% put the body of the article here
\end{document}
